---
title: 'Predicting Car Mileage: A Simple Shiny App'
author: "Nguyen Tran Hai Dang"
date: "November 14, 2025"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# Load necessary data and model for code chunks
data(mtcars)
mpg_model <- lm(mpg ~ hp, data = mtcars)
```

## Introductions
App Name: Simple MPG Predictor
Goal: Provide a quick, interactive tool to estimate a car's fuel efficiency based on its engine power.

Technologies: Shiny, R Markdown

Link to App: https://nthd65.shinyapps.io/shiny_pitch_project/

## The Challenge and The Solution 
Challenge: Estimating Fuel Efficiency
In automotive analysis, quickly assessing the MPG-HP trade-off is crucial. Our application addresses this by providing an immediate, data-driven estimate.

Our Solution: A Simple Predictive Model
We use the classic mtcars dataset and a Linear Regression Model to establish the relationship:
$$MPG \approx \beta_0 + \beta_1 \times HP$$


## Model Verification 
Core Model Statistics
The application's logic is based on this simple linear model. Here are the key coefficients from the R code evaluated during the presentation generation process:

```{r}
# Embedded R code that gets run and displayed
summary(mpg_model)$coefficients
```

Interpretation
(Intercept): The estimated MPG when HP is zero (not practically meaningful, but essential for the model).

hp: The negative coefficient (`r round(summary(mpg_model)$coefficients[2,1], 4)`) shows that for every 1 unit increase in HP, MPG decreases by about `r abs(round(summary(mpg_model)$coefficients[2,1], 4))` units.


## Application Features
Key Features of the App
Input Widget: A slider for smooth, intuitive selection of Horsepower. (Meets requirement for widget input)

Reactive Calculation: The prediction is updated instantly using the R model in server.R. (Meets requirement for calculation)

Visualization: An interactive plot displays the data and highlights the prediction point in red. (Meets requirement for reactive output)

App Screenshot

## Next Steps & Conclusion 
Conclusion
The Shiny application successfully demonstrates the ability to translate a simple statistical model into a practical, interactive web tool.

Next Steps
Integrate more predictors (e.g., Weight, Displacement) for multi-variable prediction.

Add a visual output displaying the Confidence Interval for the prediction to show uncertainty.